\documentclass[../../fulltext/fulltext.tex]{subfiles}
\begin{document}

\begin{savequote}[45mm]
	I guess I think of lotteries as a tax on the mathematically challenged.
	\qauthor{Roger Jones}
\end{savequote}

\chapter{Introduction}
The second law of thermodynamics states ...  This is often regarded as the pillar of modern physics, the one rule our universe must obey.  A natural, and valid, interpretation of this law is that we live in a chaotic, random world.  And our daily experiences reflect that.  There are billions of people, thousands of languages, billions of stars etc.  

Yet, for all this randomness, we, as humans, have become remarkably adept at muddling through the chaos, at predicting what comes next.  Even without a gift of premonition, I can largely tell how my day will go, what I will eat, when I'll finish work. I can tell what adding just the right amount of olive oil will do to my dish, without any exact measurements. With the assistance of my peers, my predictions can delve even deeper. I can predict what route to take based on the traffic, what to wear based on my weather man, which game to watch based on sports analysts, and so on.  So how have we become so good at prediction?  How can we predict finer details, such as traffic patterns, market fluctuations, or health scenarios?  Well, the answer (often) lies in the numbers.

While predictive analytics are not the end all be all, (a computer probably won't tell me who to marry), data based prediction has, and will, play a major role in our society.  

\begin{itemize}
\item Anecdote about cooking, recipes, etc.
\item Companies use analytics when they decide what movies to air, ie \emph{The Iron Giant} or \emph{Steve Jobs}
\item The history of quantitative predictions, from the Greeks earliest attempts to today's world of big data.
\item Emphasize where human intuition is still valuable, business, sports, weather, etc. 
\item The main theme of the book is how we use tools to predict what is going to happen next, ranging from quantitative tools, which are the most prevalent, but not forgetting human intuition, which is most prevalent in the Drake equation, stock markets, sports, and gambling markets. Hopefully sprinkle in anecdotes to make the more technical aspects more approachable, perhaps include some code.
\item German tank (super cool)
\end{itemize}
\end{document}